A linearization procedure for constrained multibody systems

### 2012-08-28 PetersonGedeHubbard2012.tex
Fixed a parens

The matrices which make up the linear equations were created using the method
presented in Section \ref{sec:results}. It is important to note that the
entries in these matrices must be evaluated at the point of linearization
($\bm{q}^*, \bm{\dot{q}}^*, \bm{u}^*, \bm{\dot{u}}^*$), and that this point of
linearization must satisfy the equations in Table \ref{table:assumptions}.
There is no requirement that this point be an equilibrium point, which implies
that in general both $\bm{\dot{q}}$ and $\bm{\dot{u}}$ may be non-zero. To
reduce the complexity of the equations, we chose $q_0^* = q_2^* = 0$.  This
means that the other quantities in the linearized equations (other $q$'s, the
$\dot{q}$'s, the $u$'s, and the $\dot{u}$'s need to be solved for with these 2
quantities already set to 0).

>>>>

The matrices which make up the linear equations were created using the method
presented in Section \ref{sec:results}. It is important to note that the
entries in these matrices must be evaluated at the point of linearization
($\bm{q}^*, \bm{\dot{q}}^*, \bm{u}^*, \bm{\dot{u}}^*$), and that this point of
linearization must satisfy the equations in Table \ref{table:assumptions}.
There is no requirement that this point be an equilibrium point, which implies
that in general both $\bm{\dot{q}}$ and $\bm{\dot{u}}$ may be non-zero. To
reduce the complexity of the equations, we chose $q_0^* = q_2^* = 0$.  This
means that the other quantities in the linearized equations (other $q$'s, the
$\dot{q}$'s, the $u$'s, and the $\dot{u}$'s) need to be solved for with these 2
quantities already set to 0.
